Poisson Regression

### 2019-12-10 rmds/linear_regression.Rmd
some work with a slightly different response

# should find better way to read data from rmd folder
lm_dat <- readRDS('/Users/raven/Documents/honors/honors-project/data/modeling-dat/lm_dat_scaled.RDS')
```

@@

```{r}
lm_dat <- lm_dat[!is.na(daily_boards) & !is.na(pop_density) & !is.na(emp_density) & !is.na(perc_no_veh) & !is.na(walkability) & !is.na(log_daily_stops)]
lm1 <- lm(scale(log_daily_boards) ~ pop_density + emp_density + perc_no_veh + walkability + scale(log_daily_stops), lm_dat, na.action = na.exclude)

@@

```{r}
lm_dat$predicted_log_scale_boards <- lm1$fitted.values
ggplot(lm_dat, aes(x=scale(log_daily_boards), y = predicted_log_scale_boards)) +
  geom_point() +
  labs(title = "Actual versus fitted") +
  theme_minimal() + 
  xlim(-3, 3) + ylim(-3, 3)
```

>>>>

# should find better way to read data from rmd folder
lm_dat <- readRDS('/Users/mcknigri/Documents/honors/honors-project/data/modeling-dat/lm_dat_scaled.RDS')
```

@@

```{r}
lm_dat <- lm_dat[!is.na(daily_boards) & !is.na(pop_density) & !is.na(emp_density) & !is.na(perc_no_veh) & !is.na(walkability) & !is.na(log_daily_stops)]
lm_dat[daily_boards_per_stop == 0, daily_boards_per_stop := 0.01]

lm1 <- lm((scale(log(daily_boards_per_stop))) ~ pop_density + emp_density + perc_no_veh + walkability + scale(log_daily_stops), lm_dat, na.action = na.exclude)

@@

```{r}
lm_dat$predicted_log_scale_boards <- lm1$fitted.values
ggplot(lm_dat, aes(x=scale(log(daily_boards_per_stop)), y = predicted_log_scale_boards)) +
  geom_point(alpha = 0.5) +
  geom_abline(yintercept = 0, slope = 1) +
  labs(title = "Actual versus fitted") +
  theme_minimal() 
```

### 2019-12-10 rmds/poisson_regression.Rmd
some work with a slightly different response

mod_dat <- readRDS('/Users/raven/Documents/honors/honors-project/data/modeling-dat/p_dat_scaled.RDS')
setDT(mod_dat)

@@

```{r}
mod_dat <- mod_dat[!is.na(daily_boards) & !is.na(pop_density) & !is.na(emp_density) & !is.na(perc_no_veh) & !is.na(walkability) & !is.na(daily_stops)]

y <- mod_dat$daily_boards
E <- mod_dat$daily_stops

@@

#poisson_fitsimp <- stan(poisson, data = standat1, warmup = 1000, iter = 2000)
poisson_fitsimp <- readRDS("/Users/raven/Documents/honors/honors-project/fits/poisson_fitsimp.RDS")

print(poisson_fitsimp, pars = c("mu", "betas[1]", "betas[2]", "betas[3]", "betas[4]"), probs=c(0.025, 0.5, 0.975))
#launch_shinystan(poisson_fitsimp)
```

## Predictions
```{r}
posterior <- extract(poisson_fitsimp)
yrep <- posterior$y_rep
yrep <- yrep[sample(nrow(yrep), 50), ]

pp_check(y, yrep, ppc_dens_overlay) + 
  theme_minimal() +
  xlim(0, 200) +
  labs(title = "Actual versus fitted")
```

@@

```{r}
poisson_theta <- "/Users/raven/Documents/honors/honors-project/stan/poisson_theta.stan"

poisson_theta_fit <- stan(poisson_theta, data = standat1, warmup = 7000, iter = 8000)
saveRDS(poisson_theta_fit, "/Users/raven/Documents/honors/honors-project/stan/poisson_theta_test.stan")

@@

```{r}
fit <- rstan::extract(poisson_theta_fit)
test <- rpois(fit$lambda, n = 1513)

ggplot(mod_dat, aes(x=test)) +
  geom_density(color = "red") +
  geom_density(aes(x=daily_boards*365), color = "blue") + xlim(0, 500)
```

>>>>

mod_dat <- readRDS('/Users/mcknigri/Documents/honors/honors-project/data/modeling-dat/p_dat_scaled.RDS')
setDT(mod_dat)

@@

```{r}
mod_dat <- mod_dat[!is.na(daily_boards_per_stop) & !is.na(pop_density) & !is.na(emp_density) & !is.na(perc_no_veh) & !is.na(walkability) & !is.na(daily_stops)]

y <- mod_dat$daily_boards_per_stop
E <- mod_dat$daily_stops

@@

poisson <- "/Users/mcknigri/Documents/honors/honors-project/stan/poisson.stan"

poisson_fitsimp <- stan(poisson, data = standat1, warmup = 1000, iter = 2000)
#poisson_fitsimp <- readRDS("/Users/raven/Documents/honors/honors-project/fits/poisson_fitsimp.RDS")

print(poisson_fitsimp, pars = c("mu", "betas[1]", "betas[2]", "betas[3]", "betas[4]"), probs=c(0.025, 0.5, 0.975))
launch_shinystan(poisson_fitsimp)
```

## Predictions
```{r}
posterior <- rstan::extract(poisson_fitsimp)
yrep <- posterior$y_rep
yrep <- yrep[sample(nrow(yrep), 100), ]

pp_check(y, yrep, ppc_dens_overlay) + 
  theme_minimal() +
  xlim(0, 200) +
  labs(title = "Actual versus fitted") + xlim(-1, 5)
```

@@

```{r}
poisson_theta <- "/Users/mcknigri/Documents/honors/honors-project/stan/poisson_theta.stan"

poisson_theta_fit <- stan(poisson_theta, data = standat1, warmup = 1000, iter = 2000)
saveRDS(poisson_theta_fit, "/Users/raven/Documents/honors/honors-project/stan/poisson_theta_test.stan")

@@

```{r}
fit <- rstan::extract(poisson_theta_fit)
theta_yrep <- fit$y_rep
theta_yrep <- theta_yrep[sample(nrow(theta_yrep), 100), ]

pp_check(y, theta_yrep, ppc_dens_overlay) + 
  theme_minimal() +
  xlim(0, 200) +
  labs(title = "Actual versus fitted") + xlim(-1, 5)
```
